---
title: My dynamic report
output: html_fragment
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE,
                      fig.width=9, fig.height=5)
```
```{css}
body {
  font-family: Georgia, serif;
  max-width: 900px;
  margin: auto;
  padding: 20px;
  background-color: #f9f9f9;
  color: #2c2c2c;
}

h2 {
  color: #3a5a8c;
  border-bottom: 2px solid #3a5a8c;
  padding-bottom: 6px;
}

p {
  line-height: 1.7;
}

img {
  margin-top: 20px;
  margin-bottom: 20px;
}
```

## Daily Habits: Social Media & Exercise Tracking

This report tracks daily social media usage and exercise habits logged over a two-week period of yours truly. Each entry represents one day, recorded using a personal Google Form.
```{r}
library(tidyverse)

# Import and rename data
latest_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRiBnG1C-HUsC6CXd1aWNAyxiyDFmwIY_faT_I7A8rZlD3BcoXQe9xTAgDVUt656TRLVCnXO_IBB0th/pub?gid=1037567688&single=true&output=csv") %>%
  rename(
    timestamp        = 1,
    date             = 2,
    social_media_hrs = 3,
    exercise_type    = 4,
    exercise_mins    = 5
  ) %>%
  mutate(exercised = ifelse(exercise_type %in% c("Gym", "Fencing", "Walk and Talk with other fellow humans"),
                            "Exercised",
                            "Did Not Exercise"))

# Summary values
mean_social_media <- mean(latest_data$social_media_hrs, na.rm = TRUE) %>%
  round(1)

mean_exercise <- latest_data %>%
  filter(exercised == 'Exercised') %>%
  pull(exercise_mins) %>%
  mean(na.rm = TRUE) %>%
  round(2)

mean_social_media_rest <- latest_data %>%
  filter(exercised == "Did Not Exercise") %>%
  pull(social_media_hrs) %>%
  mean(na.rm = TRUE) %>%
  round(2)

mean_social_media_exercised <- latest_data %>%
  filter(exercised == 'Exercised') %>%
  pull(social_media_hrs) %>%
  mean(na.rm = TRUE) %>%
  round(2)

total_obs <- length(latest_data$social_media_hrs)

most_common_exercise <- latest_data %>%
  count(exercise_type) %>%
  slice_max(n, n = 1) %>%
  pull(exercise_type)
```

Over the `r total_obs` days logged, the average time spent on social media was `r mean_social_media` hours per day. On active days, the average exercise duration was `r mean_exercise` minutes, with an average of `r mean_social_media_exercised` hours spent on social media. On rest days, the average social media usage was `r mean_social_media_rest` hours. The most frequently logged activity was **`r most_common_exercise`**.
```{r}
# Bar chart 1 - frequency of exercise types (sorted highest to lowest)
latest_data %>%
  ggplot() +
  geom_bar(aes(y = fct_rev(fct_infreq(exercise_type)), fill = exercise_type)) +
  labs(
    title = "Frequency of Exercise Types Logged",
    x = "Number of Days",
    y = "Exercise Type",
    caption = "Source: Daily Habit Log"
  ) +
  theme(legend.position = "none")
```
```{r}
# Bar chart 2 - average social media hours per exercise type (sorted)
latest_data %>%
  group_by(exercise_type) %>%
  summarise(avg_social_media = mean(social_media_hrs, na.rm = TRUE)) %>%
  ggplot() +
  geom_bar(aes(y = fct_reorder(exercise_type, avg_social_media),
               x = avg_social_media,
               fill = exercise_type),
           stat = "identity") +
  labs(
    title = "Average Social Media Hours by Exercise Type",
    x = "Average Hours",
    y = "Exercise Type",
    caption = "Source: Daily Habit Log"
  ) +
  theme(legend.position = "none")
```
```{r}
# Bar chart 3 - average social media hours: exercised vs did not exercise
latest_data %>%
  group_by(exercised) %>%
  summarise(avg_social_media = mean(social_media_hrs, na.rm = TRUE)) %>%
  ggplot() +
  geom_bar(aes(y = fct_reorder(exercised, avg_social_media),
               x = avg_social_media,
               fill = exercised),
           stat = "identity") +
  labs(
    title = "Average Social Media Hours: Exercised vs Did Not Exercise",
    x = "Average Hours",
    y = "",
    caption = "Source: Daily Habit Log"
  ) +
  theme(legend.position = "none")
```
